IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-07-30 review/response_2.tex

		\begin{point}
			The authors are suggested to study the impact of IRS passive beamforming on the waveform design without IRS. For example, they can show the optimized waveforms with versus without IRS to unveil the interplay between them. Or even better, analytically compare the two waveforms.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			In the introduction, it is suggested to also discuss the new design challenges posed by the nonlinear model compared to the existing designs under the linear model.
		\end{point}

		\begin{response}
			We believe this is an important issue and have modified the manuscript accordingly as follows.
			\begin{framed}
				\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model proposed in \cite{M-Clerckx2016a}. Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency compensation (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
			\end{framed}
		\end{response}

@@

		\begin{point}
			If possible, in Fig.~\ref{M-fi:re_irs_1mhz} and \ref{M-fi:re_irs_10mhz}, the authors can show the performance of the design under the conventional linear harvester model, so as to show how much performance loss it would incur.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			It was shown via simulation that PS is not always superior to TS, unlike the linear model. Is it possible to develop some analytical preconditions to determine which one is better?
		\end{point}

		\begin{response}
			We concluded that PS outperforms TS when the number of subcarrier is relatively small or when the SNR is relatively large. However, the analytical preconditions in the proposed system can be very hard to obtain because SNR can depend on many factors (e.g., distance of all paths, number of IRS elements, average noise power, etc.). Essentially, this behavior origins from the waveform selection and we would like to analyze it in a nutshell.

			TS only performs a naive time-sharing between the WIT point and the WPT point. At the WIT point, only modulated waveform is used to maximize the achievable rate. At the WPT point, the optimal waveform depends on the number of subcarriers $N$. Although the modulated waveform has an modulation gain of \num{2} that outstands for a small $N$, it creates no DC coupling between frequencies and is outperformed by multisine for a large $N$. Therefore, for a relatively small $N$, the modulated waveform is used at both WIT and WPT point, and one can heuristically infer that no multisine waveform is needed for any point (this is verified in simulation). In this case, the R-E region is convex, which aligns with the conventional linear harvester model (PS outperforms TS and dedicated power waveform is unnecessary). However, as $N$ becomes sufficiently large, multisine waveform further boosts the WPT point due to its power benefit under nonlinear harvester model. It creates some concavity in the high-power region and accounts for the superiority of TS.

			Similar effect exists for SNR. At high SNR, the SWIPT user can achieve a decent rate even if a small fraction of transmit power is allocated to the modulated waveform. Therefore, one can approach high-rate region fast at a small cost of DC power at high SNR. This is however impossible at low SNR.
		\end{response}

@@

		\begin{point}
			Some editorial comments: 1) ``a (-->an) M-antenna''; 2) ``through a (-->an) L-element IRS''; 3) ``the CSIT of direct and cascaded channels are (-->is) known''; 4) ``It demonstrated (-->demonstrates) that''; 5) In Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, the text in the y-axis is too long. Please divide it into two rows. Besides, the text in the x-axis of the upper figure is covered by the lower one.
		\end{point}

		\begin{response}
			We sincerely appreciate your careful reading and rigorous feedbacks. The manuscript have been revised accordingly and we will endeavor to avoid similar issues in the future.
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			Proposition~\ref{M-pr:bcd} is questionable. The algorithm may not converge to a local optimal due to the coupling constraint~\eqref{M-co:original_rate}.
		\end{point}

		\begin{response}
			We sincerely appreciate the reviewer for pointing out this issue. Indeed, the local optimality is not guaranteed as \eqref{M-co:original_rate} couples all blocks together. We have removed the claim on optimality and updated Proposition~\ref{M-pr:bcd} as follows.
			\begin{framed}
				For any feasible initial point, the BCD Algorithm~\ref{M-al:bcd} is guaranteed to converge.
			\end{framed}
			The proof has been modified correspondingly.
			\begin{framed}
				The objective function \eqref{M-ob:original} is non-decreasing over the iterations, because the IRS phase shift by Algorithm~\ref{M-al:sca} is local optimal, the active precoder by \eqref{M-eq:b_n} is global optimal, and the waveform amplitude and splitting ratio by Algorithm~\ref{M-al:gp} are local optimal. \eqref{M-ob:original} is also upper-bounded due to the unit-modulus constraint \eqref{M-co:original_modulus} and the transmit power constraint \eqref{M-co:original_power}. Therefore, Algorithm~\ref{M-al:bcd} is guaranteed to converge. However, it may not converge to optimal points since variables are coupled in constraint~\eqref{M-co:original_rate} \cite{M-Grippo2000}.
			\end{framed}
		\end{response}

### 2021-08-01 main.tex
:pencil: Update manuscript

		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links. $d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference\footnote{We set the AP-UE distance to be larger than SWIPT literatures \cite{Clerckx2018b} and experiments \cite{Kim2020a} thanks to the IRS.}. We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency with \SI{40}{\dB} free-space path loss at \SI{1}{\meter}. The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively. All channels are assumed Non-Line-of-Sight (NLoS) where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the taps are modeled as i.i.d. CSCG random variables. Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$ \cite{Clerckx2016a}. We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{36}{\dBm}$, the receive antenna gain as \SI{2}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region). Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

@@

		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}. \emph{First,} adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy. \emph{Second,} passive beamforming has a larger array gain and power scaling order than active beamforming. This behavior is more obvious in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector} for the case of WIT and WPT. As a reference, the Adaptive Single Sinewave (ASS) allocates all power to the multisine at the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}. For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR, which corresponds to a transmit array gain of $M$ and a doubled harvester input power. Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, which suggests an active scaling law in the order of $M^2$. On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dB}, which implies a reflect array gain of $L^2$. An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$. Hence, doubling the number of IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), corresponding to a passive scaling law in the order of $L^4$. Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link. Moreover, the ASS strategy does not exploit the harvester nonlinearity and ends up with a nearly \SI{20}{\dB} current gap compared to SMF and GP. These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the passive beamforming design.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_csi.tex}
				}
			}
			\subfloat[Quantized IRS\label{fi:re_quantization}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_quantization.tex}
				}
			}
			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$. $\epsilon_n^2 \to \infty$ corresponds to no CSIT and random IRS; $b=0$ and $b \to \infty$ correspond respectively to no IRS and unquantized IRS.}
		\end{figure}

>>>>

		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links. $d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference. The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively. We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency where the channel is modeled by IEEE TGn channel model D \cite{Erceg2004}. Specifically, the path loss exponent is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards. All fadings are modeled as Non-Line-of-Sight (NLoS) with tap delays and powers specified by model D. The tap gains are modeled as i.i.d. CSCG variables. Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$ \cite{Clerckx2016a}. We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region). Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

@@

		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}. \emph{First,} adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy. \emph{Second,} the conventional Linear Energy Harvester (LEH) model leads to power-inefficient design. To show the underlying performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that, 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required, 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}. As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} current gap compared to SMF and GP. \emph{Third,} passive beamforming has a larger array gain and power scaling order than active beamforming. This behavior is more obvious for the case of WIT and WPT. For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR, which corresponds to a transmit array gain of $M$ \cite{Tse2005} and a doubled harvester input power. Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, which aligns with the active scaling law in the order of $M^2$ \cite{Clerckx2018b}. On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dB}, which implies a reflect array gain of $L^2$ \cite{Wu2019}. An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$. Hence, doubling the number of IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), corresponding to a passive scaling law in the order of $L^4$. Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link. These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the passive beamforming design.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_csi.tex}
				}
			}
			\subfloat[Quantized IRS\label{fi:re_quantization}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_quantization.tex}
				}
			}
			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$. $\epsilon_n^2 \to \infty$ corresponds to no CSIT and random IRS; $b=0$ and $b \to \infty$ correspond respectively to no IRS and continuous IRS.}
		\end{figure}
